Kindly Bent to Free Us

### 2019-11-18 kindly/lang.tex
Fix Splitting rules on bindings.

\subsubsection{Environments and bindings}
\label{sdtyping:envs}
\begin{figure*}[tp]
  \begin{minipage}{0.28\linewidth}
    \begin{align*}
      \E &::=\ \Eempty \mid \E;B\tag{Environments}\\
      B &::=\ \bnone \tag{Empty} \\
         &\mid \bvar{x}{\schm}\tag{Variables}\\
         &\mid \bvar{\borrow{x}}{\borrowty{k}{\tau}}\tag{Borrows}\\
         &\mid \svar{x}{\schm}^n \tag{Suspended}\\
         &\mid \bvar{\tvar}{\kschm}\tag{Types}
         % |&\ \tydecl{t}{\kschm}{K}{\tau}\tag{Type Declaration}\\
    \end{align*}
    \caption{Type environments}
    \label{grammar:env}
  \end{minipage}\hfill
  \begin{minipage}{0.7\linewidth}
    \begin{mathpar}
      \ruleSDBorrow
      \and
      \ruleSDLam
      \and
      \ruleSDVar
      \and
      \ruleSDPair
      \and
      \ruleSDRegion
      \and
      \ruleSDMatchPair
    \end{mathpar}
    \caption{Selected typing rules}
    \label{selectrules:borrow}
    \label{selectrules:binders}
    \label{sdtyp:pair}
    \label{selectrules:region}
    \label{selectrules:matching}
  \end{minipage}
\end{figure*}

@@

      \Cleq{\schm}{\kun_\infty}
      &\bvar{x}{\schm}&\bvar{x}{\schm}&\bvar{x}{\schm}
      &Both\\[2mm]

      {\Cempty}&
      {\bvar{\borrow[\IBORROW]{x}}{\schm}}&
      {\bvar{\borrow[\IBORROW]{x}}{\schm}}&{\bvar{\borrow[\IBORROW]{x}}{\schm}}
      &Borrow\\[2mm]

      {\Cempty}&{\bvar{x}{\schm}}&{\bvar{x}{\schm}}&{\bnone}
      &Left\\
      {\Cempty}&{\bvar{x}{\schm}}&{\bnone}&{\bvar{x}{\schm}}
      &Right\\[2mm]

@@

    \end{tabular}
    \caption{Splitting rules for bindings}
    \label{sdtyp:split}
  % \end{minipage}
\end{figure}

@@

\cref{sdtyp:split} shows the action of the splitting rules on single
bindings. If $x$'s type is unrestricted, then
the {\sc Both} rule indicates that we can duplicate it.
Similarly, unrestricted borrows can be duplicated according to rule
{\sc Borrow}.
The {\sc Left} and {\sc Right} rules are always applicable and move a binding
either to the left or right environment.
The rules {\sc Susp} and {\sc SuspB} split off suspended bindings to
the left while conserving access to the binding on the right.
A suspended binding can later be turned
into a borrow inside a region. Splitting of suspended bindings is
asymmetric. It must follow the order of execution from left to right,
which means that a resource can be used first as a borrow on the left
and then later as a full resource on the right. The {\sc Susp} rule
works with a full resource while the {\sc SuspB}
rule splits off an shared suspended binding from a borrow.
%
Splitting applies whenever an
expression has multiple subexpressions:  pairs, function applications,
and let bindings. In the
expression
$\letin{a}{\text{create}\ 10\ x}
{\introPair{\region[{}]{\Sone x\IBORROW}{\app{\text{length}}{\borrow[\IBORROW]{a}}}}{a}}$,
the rule {\sc Susp} splits off a borrow from  the resource
\lstinline/a/ to use it in the left component of the pair.
As usual, a borrow cannot be active in the same scope as its resource.
The \emph{region} around its use ensures that the borrow in the left component does not
escape, which brings us to the next topic.

>>>>

\subsubsection{Environments and bindings}
\label{sdtyping:envs}
\begin{figure*}[tp]
  \begin{minipage}{0.28\linewidth}
    \begin{align*}
      \E &::=\ \Eempty \mid \E;B\tag{Environments}\\
      B &::=\ \bnone \tag{Empty} \\
         &\mid \bvar{x}{\schm}\tag{Variables}\\
         &\mid \bvar{\borrow{x}}{\borrowty{k}{\tau}}\tag{Borrows}\\
         &\mid \svar{x}{\schm}^n \tag{Suspended}\\
         &\mid \bvar{\tvar}{\kschm}\tag{Types}
         % |&\ \tydecl{t}{\kschm}{K}{\tau}\tag{Type Declaration}\\
    \end{align*}
    \caption{Type environments}
    \label{grammar:env}
  \end{minipage}\hfill
  \begin{minipage}{0.7\linewidth}
    \begin{mathpar}
      \ruleSDBorrow
      \and
      \ruleSDLam
      \and
      \ruleSDVar
      \and
      \ruleSDPair
      \and
      \ruleSDRegion
      \and
      \ruleSDMatchPair
    \end{mathpar}
    \caption{Selected typing rules -- $\inferS{C}{\E}{e}{\tau}$}
    \label{selectrules:borrow}
    \label{selectrules:binders}
    \label{sdtyp:pair}
    \label{selectrules:region}
    \label{selectrules:matching}
  \end{minipage}
\end{figure*}

@@

      \Cleq{\schm}{\kun_\infty}
      &\bvar{x}{\schm}&\bvar{x}{\schm}&\bvar{x}{\schm}
      &Both\\

      {\Cempty}&
      {\bvar{\borrow[\IBORROW]{x}}{\schm}}&
      {\bvar{\borrow[\IBORROW]{x}}{\schm}}&{\bvar{\borrow[\IBORROW]{x}}{\schm}}
      &Borrow
      % \\

      % {\Cempty}&
      % \svar[\IBORROW]{x}{\schm}^n&\svar[\IBORROW]{x}{\schm}^n&\svar[\IBORROW]{x}{\schm}^n
      % &BothS
      \\[2mm]

      {\Cempty}&{b_x}&{b_x}&{\bnone}
      &Left\\
      {\Cempty}&{b_x}&{\bnone}&{b_x}
      &Right\\[2mm]

@@

      {\Cempty}&
      {\svar{x} \schm}&{\svar[\IBORROW] x \schm^n}&{\svar{x} \schm}
      &SuspS\\
    \end{tabular}
    \caption{Splitting rules for bindings -- $\lsplit{C}{B}{B_l}{B_r}$}
    \label{sdtyp:split}
  % \end{minipage}
\end{figure}

@@

\cref{sdtyp:split} shows the action of the splitting rules on single
bindings. If $x$'s type is unrestricted, then
the {\sc Both} rule indicates that we can duplicate it.
Similarly, unrestricted borrows can be duplicated according to rule
{\sc Borrow}.
The {\sc Left} and {\sc Right} rules are always applicable and move a binding
either to the left or right environment.
The rules {\sc Susp}, {\sc SuspB} and {\sc SuspS}
split off suspended bindings to
the left while conserving access to the binding on the right.
A suspended binding can later be turned
into a borrow inside a region. Splitting of suspended bindings is
asymmetric. It must follow the order of execution from left to right,
which means that a resource can be used first as a borrow on the left
and then later as a full resource on the right. The {\sc Susp} rule
works with a full resource, the {\sc SuspB}
with a borrow and {\sc SuspS} with a suspended binding.
%
Splitting applies whenever an
expression has multiple subexpressions:  pairs, function applications,
and let bindings. In the
expression
$\letin{a}{\text{create}\ 10\ x}
{\introPair{\region[{}]{\Sone x\IBORROW}{\app{\text{length}}{\borrow[\IBORROW]{a}}}}{a}}$,
the rule {\sc Susp} splits off a borrow from  the resource
\lstinline/a/ to use it in the left component of the pair.
As usual, a borrow cannot be active in the same scope as its resource.
The \emph{region} around its use ensures that the borrow in the left component does not
escape, which brings us to the next topic.
